; Azazel Customizable by RenanMsV changes and addons by Aruhito_0 for CoC 1.4.22 may work with other
[azazel_config]
	;use true or false

	fix_bleeding = true 		; default = false This will fix the bleeding, radiation, hunger glitch from default Azazel
	disable_animation = true 	; default = false This will remove the animation between the transition to a new person. Instant transition.
	invul_time = 10 			; default = 10 This will set the invulnerable_time in seconds between the transition to a new person. (so you dont get shot again instantly, lower values increase the risk of carying over bleed and animation)
	faction_spawn = true 		; default = false With this option turned true your azazel mod will search for faction mates if no squad mate is left. (may cause problems)
	stay_on_map = false 		; NOT WORKING default = false This should ensure that you stay in the same location. 
	debugMessages = false 		; debug
	
[azazel_tasks]
	;ONLY USE ONE OPTION

	keep_tasks_squad = true 	; default = false With this option you will only fail tasks if whole squad is dead (recommended).
	keep_tasks_faction = false 	; default = false With this option you will keep your tasks as long as you spawn as faction mate.
	keep_tasks_always = false 	; default = false Never lose tasks on death (not recommended).
	fail_tasks = false 			; default = true  Fail tasks on death like vanilla azazel mode.

[azazel_money]
	;use true FOR ONE option and false for OTHERS
	;Gain Money system will have a higher priority in case one or more are enabled at the same time.
	;function handle_actor_money

	gain_money = false	 		; Enable default system that you get about 2000 RU when you die.
	lose_all_money = false 		; Enable new system that you lose all your money when you die and respawn with about 500 RU (as a new game does). You cant get the money back
	stalker_money = true		; Enable new system that you will respawn with the NPC's money.
	keep_money_squad = false	; The squad leader passes the money on. Only lose money if your squad is erased.
	never_loose_money = false	; Never lose any money Azazel has gained.
	
[azazel_extra_supplies]
		;this grants you some extra supplies after deat when entering a new character
	
	activate_supplies = false	;activate the system to receive extra supplies for the new character
	
		;Enter number between 0 and 100 to set the chance (0= never get item, 100 always get item, 50 = 50% chance, fliping a coin)
	
	give_medkit = 75		; default = 75
	give_bandage = 97		; default = 97
	give_vinca = true		; when no bandage is given you can receive vinca if you like
	give_bread = 90			; default = 90
	give_vodka = 95			; default = 95